Applying Renormalization Group Theory to the Square Well Liquid

### 2014-05-20 papers/thesis-roth/project.tex
updates to project report Tested on elliot. Took 0:21.08.

\subsection{Thermodynamic perturbation theory}\label{subsec:TPT}
\fixme{Add here an introduction to thermodyamic perturbation theory,
  explaining $a_1$ and $a_2$ and their ``exact'' formulas that we wish
  to approximate.}

\fixme{And introduction to TPT---why do we use it?}

\fixme{For now, the discussion follows entirely from the Simple Liquids book\cite{Hansen06}}

The pair potential $v(\1,\2)$ describes the interaction between two hard spheres. For the square-well model,
\begin{align}
  v_\text{SW}(\1,\2) &=
    \begin{cases}
      \infty & r < \sigma \\
      -\epsilon & \sigma < r < \lambda\sigma \\
      0 & \lambda\sigma < r
    \end{cases}
\end{align}

@@

\section{Conclusion}
I have implemented a the use of renormalization group theory in calculations for the square well liquid. The program is not entirely de-bugged.

>>>>

\subsection{Thermodynamic perturbation theory}\label{subsec:TPT}

\fixme{And introduction to TPT---why do we use it?}
This discussion follows primarily from \textit{Theory of Simple Liquids}, by Hansen and McDonald\cite{Hansen06}.

Thermodynamic perturbation theory treats the intermolecular potential as separable into two parts, one for short-range repulsion and another for long-range attraction.

The pair potential $v(\1,\2)$ describes the interaction between two hard spheres. For the square-well model, the pair potential is
\begin{align}
  v_\text{SW}(\1,\2) &=
    \begin{cases}
      \infty & r < \sigma \\
      -\epsilon & \sigma < r < \lambda\sigma \\
      0 & \lambda\sigma < r
    \end{cases}
\end{align}

@@

\section{Conclusion}
I have implemented a the use of renormalization group theory in calculations for the square well liquid. The program is not entirely de-bugged. I have also developed an algorithm that calculates liqiud-vapor coexistence curves, even close to the critical point.
